### Codebook

#### Variable list and descriptions

Variable name    | Description
-----------------|------------
subject          | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.
activity         | Activity name
featDomain       | Feature: Time domain signal or frequency domain signal (Time or Freq)
featInstrument   | Feature: Measuring instrument (Accelerometer or Gyroscope)
featAcceleration | Feature: Acceleration signal (Body or Gravity)
featVariable     | Feature: Variable (Mean or SD)
featJerk         | Feature: Jerk signal
featMagnitude    | Feature: Magnitude of the signals calculated using the Euclidean norm
featAxis         | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
featCount        | Feature: Count of data points used to compute `average`
featAverage      | Feature: Average of each variable for each activity and each subject

#### Dataset structure
```{r}
str(dtTidy)
```

#### Listing the key variables in the data table
```{r}
key(dtTidy)
```

#### Showing a few rows of the dataset
```{r}
dtTidy
```

#### Summary of variables
```{r}
summary(dtTidy)
```

#### Listing all possible combinations of features
```{r}
dtTidy[, .N, by=c(names(dtTidy)[grep("^feat", names(dtTidy))])]
```

#### Saving to file
```{r save}
f <- file.path(path, "tidy_dataset.txt")
write.table(dtTidy, f, quote=FALSE, sep="\t", row.names=FALSE)
```
